---
title: "Group Project"
output: html_document
---
# Reading in Data and Plotting
```{r}
library(tidyverse)
library(tuneR)
library(ggplot2)
dir <- "data"
all_files <- list.files(dir)

wave_files <- list()
timeSeq = list()
for (i in all_files) {
  
  wave_files[[i]] <- tuneR::readWave(file.path(dir, i))
  timeSeq[[i]] <- seq_len(length(wave_files[[i]]))/wave_files[[i]]@samp.rate
  plot(timeSeq[[i]], wave_files[[i]]@left, type = "l", ylab="Signal", xlab="Time(seconds)", main = file.path(dir, i ))
}

```
# Testing on smallest file
```{r}
test_short = readWave("data/Ashwin1.wav")
time_test_short <- seq_len(length(test_short))/test_short@samp.rate 
```

# Eye movement function, need to decide on threshold, window size etc

```{r}
eye_movement_ZC = function(Y, time, 
                           windowSize = 0.5, 
                           thresholdEvents = 20,
                           downSampleRate = 50) {
  
  ## down sample
  ind = seq_len(which(time == round(time[length(time)] - windowSize, 4)) + 1)
  ind = seq(1, ind[length(ind)], by = downSampleRate)
  
  ## time vector for middle of each window
  timeMiddle <- time[ind] + windowSize/2 
  testStat = rep(NA, length(ind))
  
  ## calculate zero-crossings
  for (i in 1:length(ind)) {
    Y_subset <- Y[time >= time[ind[i]] & time < time[ind[i]] + windowSize]
    testStat[i] <- sum(Y_subset[1:(length(Y_subset) - 1)] * Y_subset[2:(length(Y_subset))] <= 0)
  }
  
  ## using threshold to determine eye movement intervals
  predictedEvent <- which(testStat < thresholdEvents)
  eventTimes <- timeMiddle[predictedEvent] # map back to the time of this 
  gaps <- which(diff(eventTimes) > windowSize )
  
  ## estimate event_time_interval
  event_time_interval <- min(eventTimes)
  for (i in 1:length(gaps)) {
    event_time_interval <- append(event_time_interval, 
                                  c(eventTimes[gaps[i]],
                                    eventTimes[gaps[i] + 1]))
  }
  event_time_interval <- append(event_time_interval, max(eventTimes))
  event_time_interval <- matrix(event_time_interval, ncol = 2, byrow = TRUE)
  
  predictedEventTimes <- rep(FALSE, length(Y))
  for (i in 1:nrow(event_time_interval)) {
    predictedEventTimes[event_time_interval[i, 1] <= time & event_time_interval[i, 2] >= time] <- TRUE
  }
  
  num_event <- length(gaps) + 1
  return(list(num_event = num_event, 
              predictedEventTimes = predictedEventTimes,
              predictedInterval = event_time_interval))
}

## Testout the function
eye_movement_ZC(Y = test_short @left, time = time_test_short)$predictedInterval
```
Seems to not be working correctly as its showing more events than are on Ashwin1_label.txt. 
# Function to extract signals 
```{r}
extractSignal = function(limits, seq, xtime) {
index = (xtime > limits[1]) & (xtime < limits[2])
return(seq[index])
}
# wave_seq = list()
# for(i in 1:length(wave_files)) {
# print(i)
# wave_file= wave_files[[i]]
# Y = wave_file@left
# xtime = seq_len(length(wave_file))/wave_file@samp.rate 
# cut_result = eye_movement_ZC(Y, xtime)
# wave_seq[[i]] = apply(cut_result$predictedInterval, 1, extractSignal, Y, xtime)
# }
```
```{r}
extractSignal = function(limits, seq, xtime) {
index = (xtime > limits[1]) & (xtime < limits[2])
return(seq[index])
}
wave_seq = list()

Y = test_short@left

cut_result = eye_movement_ZC(Y, time_test_short)
wave_seq = apply(cut_result$predictedInterval, 1, extractSignal, Y, xtime)


```


# Function for determining left or right 
```{r}
LR_detection = function(seq) {
maxval = which.max(seq)
minval = which.min(seq)
movement = ifelse(maxval < minval,  "L", "R")
return(movement)
}
```

# Insert someone's working streaming classifier function from assignment (never got mine to work)
```{r}
streaming_classifier = function(wave_file,
                                window_size = wave_file@samp.rate,
                                increment = window_size/3) {
  Y = wave_file@left
  xtime = seq_len(length(wave_file))/wave_file@samp.rate
  df= data.frame( Y=Y, time = xtime)
  predicted_labels = c()
  lower_interval = 1
  max_time = max(xtime)*window_size

  while(max_time > lower_interval + window_size)
  {
    upper_interval = lower_interval + window_size
    interval = Y[lower_interval:upper_interval]
    events = eye_movement_ZC(Y = interval, time = xtime[lower_interval:upper_interval])$predictedInterval
    if (length(events) != 0) {predicted = LR_detection(extractSignal(events, Y, xtime))}



      predicted_labels = c(predicted_labels, predicted)

    lower_interval = lower_interval + increment
  } ## end while

}## end function
```




```{r}
test_short = readWave("data/Ashwin1.wav")
time_test_short <- seq_len(length(test_short))/test_short@samp.rate 
streaming_classifier(wave_file = test_short)$predicted_labels
```

